\documentclass[../main.tex]{subfiles}
\pagenumbering{roman}
\begin{document}
\begin{center}
    \Large{\textbf{ACKNOWLEDGMENT}}\\
\end{center}
\vspace{1cm}
Completing this thesis has been a meaningful and unforgettable journey. During four months of research and writing this thesis, and four years of study at HUST, I have received support and guidance from many individuals and institutions. I would like to take this opportunity to express my sincere gratitude to all those who have contributed to the completion of this thesis.

First and foremost, I would like to express my deepest gratitude to all my professors and instructors over the past four years. I am sincerely grateful for your guidance, dedication, and encouragement, which have greatly influenced my academic journey and personal growth. 

Secondly, I would like to thank my thesis advisors, Dr. Dang Tuan Linh and Mr. Nguyen Dang Duy, for their guidance, patience, and continuous support throughout this research. I feel truly fortunate to have had the opportunity to learn from them.

I would also like to extend my heartfelt thanks to my family and my partners. Thank you for always supporting and believing in me, for encouraging me to keep moving forward, and for giving me the confidence to pursue what I truly love.

Finally, I would like to thank to all of my friends, lab mates, and everyone who has supported me along the way. Thank you all for being a part of this journey and for making it meaningful and fulfilling.
\end{document}